\huge Tor's Usability for Censorship Circumvention

### 2016-04-29 pets2017-paper/pets2017-paper.tex
Cite Xlab.
Make this a \url.

\subsection{Setup}
We ran our experiment at Xlab, the Experimental Social Science Laboratory at the University of 
California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using Xlab.

@@

\noindent https://github.com/lindanlee/circumvention-ux-tor

>>>>

\subsection{Setup}
We ran our experiment at Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of 
California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using Xlab.

@@

\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
